He-Man: A domain-specific language for lightweight concurrency

### 2011-12-13 report/report.tex
More

He-Man is most similar to Li and Zdancewic's Haskell implementation of a hybrid
event/thread programming model for network applications \cite{LiZdancewic}.
Their project has similar goals to ours, but is implemented entirely within
Haskell. As a result, unlike He-Man, the entire application must be written in
Haskell, and incurs runtime overhead from the Haskell system.

@@

Event loops are a good way to get the level of concurrency that you need

we don't need arbitrary interleaving of instructions,

@@

I/O time (both network and disk) dominates the computation time

>>>>

He-Man is most similar to Li and Zdancewic's Haskell implementation of a hybrid
event/thread programming model for network applications \cite{LiZdancewic}.
Their project has similar goals to ours, but is implemented entirely within
Haskell. As a result, unlike He-Man, their framework requires entire
applications to be written in Haskell, and incurs runtime overhead from the
Haskell system.

@@

Networking applications require a very constrained form of concurrency. Because
I/O (both network and disk) latency dominates the computation time, each
client's thread of execution spends most of its time waiting on I/O. In
particular, we would like to always yield to a client no longer blocked on I/O;
we need not yield to blocked clients, nor do we need arbitrary interleaving of
execution.

As of version 2.5.44, Linux has supported \t{epoll} for non-blocking
multiplexing I/O. A server can register any number of file descriptors with
\t{epoll\_ctl}, and a call to \t{epoll\_wait} returns the ready descriptors. In
the event loop model, all blocking I/O occurs in a single loop which

Event loops are a good way to obtain this 
to get the level of concurrency that you need

@@
